Using Fundamental Measure Theory to treat the Pair Distribution Function of the Inhomogeneous Hard-Sphere Fluid

### 2013-08-22 papers/pair-correlation/paper.tex
beautify triplet plots Tested everything on bingley.

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ plotted when $\rr_1$ and $\rr_2$ are
    in contact.}\label{fig:triplet-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-4.pdf}
  \caption{Pretty plot of the pair distribution function near a hard
    wall.}\label{fig:triplet-distribution-4}
\end{figure}

@@

    + \mathop{\mathop{\sum_{i<j}}_{k<}}_{kl \ne ij}

@@

  + \mathop{\mathop{\sum_{k<l}}_{m<n}}_{kl\ne mn}

@@

  N^2\iiiint \Theta(\sigma+\delta-r_{12})

@@

  - \frac{N^3}{2}\iiiint

@@

  \shoveleft{\quad= nN \int_{\sigma}^{\sigma+\delta} g(r) d\rr }
  - \frac{n^2N}{2} \left(\int_{\sigma}^{\sigma+\delta} g(r)

@@

  + \frac{n^3N}{6} \left(\int_{\sigma}^{\sigma+\delta} g(r)
  d\rr\right)^3 + \cdots

>>>>

\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-3.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted lin on the plot to the
    left.}\label{fig:triplet-distribution-3}
\end{figure}
\begin{figure}
  \includegraphics[width=\columnwidth]{figs/triplet-correlation-alt-4.pdf}
  \caption{The triplet distribution function
    $g^{(3)}(\rr_1,\rr_2,\rr_3)$ at packing fraction 0.3, plotted when
    $\rr_1$ and $\rr_2$ are in contact.  The color plot on the left
    shows the triplet distribution function, with white corresponding
    to the contact value of the \emph{pair} distribution function.
    The plot on the right shows the value of $g^{(3)}$ along the path
    shown as a dotted lin on the plot to the
    left.}\label{fig:triplet-distribution-4}
\end{figure}

@@

    + \frac{1}{2}\mathop{\mathop{\sum_{i<j}}_{k<l}}_{kl \ne ij}

@@

  + \frac{1}{2}\mathop{\mathop{\sum_{k<l}}_{m<n}}_{kl\ne mn}

@@

  \frac{N^2}{2}\iiiint \Theta(\sigma+\delta-r_{12})

@@

  - \frac{N^4}{8}\iiiint

@@

  \shoveleft{\quad= \frac{nN}{2} \int_{\sigma}^{\sigma+\delta} g(r) d\rr }
  - \frac{n^2N^2}{8} \left(\int_{\sigma}^{\sigma+\delta} g(r)

@@

  + \cdots
